---
title: "Quiz_05_TakeHome"
author: "Kaden Pickering"
date: "2/22/2022"
output: html_document
---

“All work presented is my own, and I have followed all rules for collaboration.”

I worked with Claire Dudley on this quiz. 

## Question 1.  Construct a graph that uses the number of Facebook friends each student has. 

```{r}
library(tidyverse) 
statsurvey_df <- read_csv("data-2/stat113_survey.csv")

# filter out NA's and 0's 
friends_plot <- statsurvey_df %>%
  filter(!is.na(Facebook)) %>%
  filter(!Facebook == "0") 
```

```{r}
stat_facebook <- 
  friends_plot %>%
  mutate(time_both = fct_inorder(time_both)) %>%
  group_by(time_both) %>%
  summarise(meanfb = mean(Facebook), 
            sdfb = sd(Facebook), 
            nfb = n()) %>%
  mutate(l_se = meanfb - sdfb / sqrt(nfb),
         u_se = meanfb + sdfb / sqrt(nfb)) 
  

ggplot(data = stat_facebook, aes(x = time_both, y = meanfb)) + 
  geom_point() +
  geom_errorbar(aes(ymin = l_se, ymax = u_se)) +
  labs(x = "Semester", y = "Average Facebook Friends")
```

## Question 2. Construct a graph that uses the proportion of students that have Facebook (assuming that 0 friends means that the student does not have a Facebook account and more than 0 friends means that the student does have a Facebook account).

```{r}
HaveFacebook <- statsurvey_df %>%
  filter(!is.na(Facebook)) 

HaveFacebook$hasfacebook = with(HaveFacebook, ifelse(Facebook > 0, 1, 0))
```

```{r}
HaveFacebook <- 
  HaveFacebook %>%
  mutate(time_both = fct_inorder(time_both)) %>%
   group_by(time_both) %>%
   summarise(meanhasfb = mean(hasfacebook),
             sdhasfb = sd(hasfacebook),
             nhasfb = n()) %>%
   mutate(l_se = meanhasfb - sdhasfb / sqrt(nhasfb),
          u_se = meanhasfb + sdhasfb / sqrt(nhasfb))
```

```{r}
ggplot(data = HaveFacebook, aes(x = time_both, y = meanhasfb)) + 
   geom_point() +
   geom_errorbar(aes(ymin = l_se, ymax = u_se)) +
   labs(x = "Semester",
        y = "Proportion of Students with Facebook")
```

