---
title: "Quiz_04_inclass"
author: "Kaden Pickering"
date: "2/16/2022"
output: html_document
---

“All work presented is my own. I have not communicated with or worked with anyone else on this quiz.”

```{r}
library(tidyverse)
library(here)
alcohol_df <- read_csv(here("data-2/alcohol.csv"))
world_df <- ggplot2::map_data("world")
```

# Question 1 

```{r}
world_df <-
   world_df %>%
   rename("country" = "region")
```

```{r}
alcohol_joined <-
   left_join(world_df, alcohol_df,
             by = "country")
```

```{r}
library(leaflet)
library(maps)
library(devtools)

ggplot(data = alcohol_df,
            mapping = aes(x =long, y = lat,
                          group = group, fill = beer_servings)) +
  geom_polygon( color = "blue") +
  coord_map(projection = "globular") +
  theme_void() + 
  scale_fill_viridis_b()

```
# couldn't get it to work but think im on the right track so it wouldn't knit unfortunately. 
# Question 2. 

If i were to use something other than a map, I'd want to look at something like a timeline or barchart. In a timeline, I'd like to see how much is consumed everyday by these countries and in a barchart just to compare them easily side by side. 
